Variations on a Bayesian Theme: Comparing Bayesian Models of Referential Reasoning

### 2013-10-14 06_conclusion.tex
cross-ref & conclusion

Our experiment and model comparison suggest the following: (1) on the conceptual level, 
it is helpful to clarify the distinction between belief, goal and action, and by systematically examining each component in the formal model we can more explicitly spell out the underlying assumptions and formulate alternatives to be tested. (2) on the empirical level, we tested the RSA model with a family of alternatives on a forced-choice experiment and investigated the speaker's preference as well as the listener's perceptual salience. Our data seem to suggest a different story about common knowledge --- what is commonly known is the Gricean pragmatic components, while both sides have his own private bias unknown to the other.

>>>>

Our experiment and model comparison suggest the following: (1) On the conceptual level, 
it is helpful to clarify the distinction between belief, goal and action, and the Bayesian framework provides us with a natural way to structure these components into a formal model. By examining each component systematically, we can explicitly spell out the underlying assumptions and formulate alternative hypotheses to be tested. (2) On the empirical level, we tested the RSA model with a family of variants motivated from the game-theoretic pragmatic perspectives on communication, and in particular, we investigated the speaker's preference as well as the listener's perceptual salience. Our data showed a more intricate picture about the roles various factors play in pragmatic reasoning about referential expressions --- what is commonly known is the Gricean pragmatic components, while either side have his own private bias unknown to the other. Also, an action-based view might better reflect the goal of communication, at least in the forced-choice experimental setting.
